A Phenomenological Model for the Intra-Cluster Medium that matches X-ray and Sunyaev-Zel'dovich observations

### 2013-08-22 paper1.tex
last Fabio version

\voffset-0.5in

@@

{\bf Our original motivation to build such a mock catalog is to predict the 
non-thermal emission at radio and gamma-ray frequencies of a cosmological 
complete sample of galaxy clusters. This is presented in a companion 
paper (REF, hereafter Paper~2).
The two basic ingredients of the two works are an $N$-body, \emph{DM-only}
cosmological simulation that we use in constructing our complete cluster sample,
and the (non-)thermal emission model. Here, we use the MultiDark simulation that
will be described in Section~\ref{sec:2}, along with our final cluster sample. As described 
in Paper~2, for any given cluster, the necessary ingredients for the non-thermal emission 
model are mass, temperature, and gas density distribution. We assign to
each cluster in that simulation a gas density profile that is phenomenologically
constructed from state-of-art X-ray observations, as will be shown in
Section~\ref{sec:3}. In Section~4 and 5, we will show that this approach can successfully
reproduce the known X-ray cluster characteristics, such as the X-ray luminosity
function (XLF), the luminosity-mass relation, $L_{\rmn{X}}- M$, and the
$Y_{\rmn{X}}-M$ relation, where $Y_{\rmn{X}}=M_\rmn{gas}k_{\rmn{B}}T$ with an
X-ray-derived gas mass $M_{\rmn{gas}}$ and temperature $T$
\citep{2006ApJ...650..128K}. Moreover, we compare our $Y_{\rmn{SZ}}-M$ relation
with SZ-derived measurements. Only if our model matches available cluster data
on the gas properties, we can safely use it in Paper~2.} In this work, the cluster mass $M_{\Delta}$ 
and radius $R_{\Delta}$ are defined with respect to a density that is $\Delta=200$ or 
$\Delta=500$ times the \emph{critical} density of the Universe. We adopt density 
parameters of $\Omega_{\rmn{m}}=0.3$, $\Omega_{\Lambda}=0.7$ and today's 
Hubble constant of $H_0 = 100 \times h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MultiDark simulation and final cluster sample}
\label{sec:2}
The MultiDark simulation used in this work is described in detail in \cite{2011arXiv1104.5130P}.  
It is an $N$-body cosmological simulation done with
the Adaptive-Refinement-Tree (ART) code \citep{1997ApJS..111...73K} of
$2048^3$ particles within a ($1000$~Mpc~$h^{-1}$)$^3$ cube. The latest WMAP5 and
WMAP7 cosmological parameters were used. This simulation is particularly well
suited for our purpose because of its large number of clusters.

@@

{\bf In Paper~2, we present predictions for the LOFAR radio observatory\footnote{www.lofar.org} 
which is expected to detect diffuse radio emission in clusters up to redshift $z \approx 1$ (e.g.,
\citealp{2010A&A...509A..68C,2012JApA..tmp...34R}).} 
Thus, we make use of different simulation snapshots up to $z=1$. 
{\bf The extrapolation of our model beyond this redshift is rather uncertain as it is based
on observations at low(er) redshift.}
In Table~\ref{tab:z}, we show the total cluster number in our final cluster sample at different redshifts.

@@

\begin{figure} 
\centering
\includegraphics[width=0.5\textwidth]{figures/gas_profiles.eps}
\caption{Electron density profiles of the 31 clusters in the REXCESS sample. Grey and black lines represent NCCCs and CCCs, respectively. The blue and red lines represent our GNFW mean profile for the NCCCs and CCCs, respectively.}
\label{fig:gas_profiles}
\end{figure}

@@

\begin{figure*} 
\centering
\includegraphics[width=0.33\textwidth]{figures/lx_m.eps}
\includegraphics[width=0.33\textwidth]{figures/yx_m.eps}
\includegraphics[width=0.33\textwidth]{figures/sz_m.eps}
\caption{X-ray and SZ scaling relations. Grey triangles show the MultiDark
  sample (limited to the mass range covered by observations), the black line is
  the corresponding scaling relation, and the blue line is the
  observational result. The black crosses represent the median values of the
  quantity in question for a given mass bin (indicated by horizontal error
  bars), and the vertical error bars represent the standard deviation within a
  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
  relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. \emph{Center.}
  $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
  observational sample by \protect\cite{2010MNRAS.406.1773M}. \emph{Right.}
  $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.18$ in comparison
  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
  median redshift of $0.18$. The bottom panels show the relative difference to
  the observational scaling relations.}
\label{fig:X_LM}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{X-ray and SZ scaling relations}
\label{sec:4}

@@

In the middle panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{X}}-M_{500}$ relation of our sample to observational data
\citep{2010MNRAS.406.1773M}. The model agrees nicely at the high-mass end, but
underpredicts the observed scaling at low masses by about $20\%$ (at the
1-$\sigma$ level). This is the same level of deviation from the data as in the
case of $L_{\rmn{X}}$, which is more significant due to the smaller scatter in
the $Y_{\rmn{X}}$ relation. The differential contribution to the thermal energy
per logarithmic interval in radius (and hence to the integrated Compton-$y$
parameter) is given by $\dd Y /\dd\log r \propto r^3 P_{\rmn{th}}(r)$, with the
thermal gas pressure $P_{\rmn{th}}=n_{\rmn{gas}}k_{\rmn{B}}T$. It peaks at
scales slightly smaller than $R_{500}$ with 1-$\sigma$ contributions extending
out to $3\,R_{500}$ \citep{2010ApJ...725...91B}. Hence, the observational
scaling constrains our model on those large scales, quite complementary to the
X-ray luminosity. The deviations at small masses either indicates different
assumptions about $f_{\rmn{gas}}$, the gas temperature, or different selection
effects of either observational sample that we use for model calibration and
comparison.  \cite{2010MNRAS.406.1773M} determine their masses by adopting a
constant value for $f_{\rmn{gas}}$, in contrast to our approach which adopts the
observed $f_{\rmn{gas},500}-M_{500}$ relation given by
\cite{2009ApJ...693.1142S}. Additionally, we adopt the
\cite{2010MNRAS.406.1773M} \emph{centrally included} temperature throughout all
our work, while \cite{2010MNRAS.406.1773M} use the \emph{centrally excised}
temperature to calculate $Y_{\rmn{X}}$. This assumption also impacts the scatter
of the $Y_{\rmn{X}}-M$ relation. In fact, using the \emph{centrally included}
temperature, we found a scatter of $\sigma_{yx} \approx 0.11$ (see
Table~\ref{tab:YXfits} where our $Y_{\rmn{X}}$ scaling relations are reported),
significantly higher than the value of $\sigma_{yx} = 0.052$ found by
\cite{2010MNRAS.406.1773M}.

In the right panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
\citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the 
\emph{Planck} Cosmo sample with Malmquist bias correction (see their Table~A.1),
which has a median redshift of $0.18$. Hence, we compare the data to our relation 
at the MultiDark snapshot $z=0.18$ (that contains 11105 clusters 
above our mass cut) which however is not used throughout the rest of the work}. Our
model reproduces the data remarkably well, except for the high-mass end where
our simulations have a weaker constraining power due to the smaller box size in
comparison to the survey volume of {\em Planck}.  We find a scatter of
$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
$\sigma_{yx} \approx 0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
relations for different redshifts.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{X-ray luminosity function}
\label{sec:5}

Studies of the XLF got out of fashion during the last years due to the
difficulties of using the X-ray luminosity for cosmological purposes. The X-ray
emissivity scales with the square of the gas density, which makes it subject to
density variations and clumping. This implies large scatter that causes a large
Malmquist bias and underlines the necessity of careful mock surveys that need to
address all systematics.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}
We thank Anders Pinzke for many useful discussions. 
%We thank Lawrence Rudnick
%and Shea Brown for a reanalysis of their
%352~MHz radio map of Coma, and for useful discussions. We thank Matteo
%Murgia for kindly providing the radio surface brightness profiles of Ophiuchucs
%and Abell~2163 that have been recomputed with respect to the Reiprich \&
%B\"{o}ringher (2002) cluster positions, and Wolfgang Reich for providing the
%1.4~GHz radio map of Coma.  
We also thank Harald Ebeling, Stefan Gottl{\"o}berg,
Anatoly Klypin, Andrey Kravtsov, Adam Mantz, Frazer Pearce, Miguel-Angel Perez
Torres, Huub R{\"o}ttgering, Jos\'e Alberto Rubi\~no, and Gustavo Yepes, for the
useful discussions and advices. Finally, we thank the MultiDark database
people, in particular Adrian Partl and Kristin Riebe. 
F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of the 
program ``Junta para la Ampliaci\'on de Estudios'' co-financed by the FSE. 
F.Z.{\ }acknowledges the hospitality of the Leiden Observatory during his stay.
F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's Consolider-Ingenio 2010 Programme under
grant MultiDark CSD2009-00064. C.P.{\ }gratefully acknowledges financial support
of the Klaus Tschira Foundation. The MultiDark Database used in this paper and
the web application providing online access to it were constructed as part of
the activities of the German Astrophysical Virtual Observatory as result of a
collaboration between the Leibniz-Institute for Astrophysics Potsdam (AIP) and
the Spanish MultiDark Consolider Project CSD2009-00064. The Bolshoi and
MultiDark simulations were run on the NASA's Pleiades supercomputer at the NASA
Ames Research Center.

>>>>

%\voffset-0.5in

@@

{\bf Our original motivation to build such a mock catalog is to predict the 
non-thermal emission at radio and gamma-ray frequencies of a cosmological 
complete sample of galaxy clusters. This is presented in a companion 
paper (REF, hereafter Paper~2).
The two basic ingredients of the two works are an $N$-body, \emph{DM-only}
cosmological simulation that we use in constructing our complete cluster sample,
and the (non-)thermal emission model. Here, we use the MultiDark simulation that
will be described in Section~\ref{sec:2}, along with our final cluster sample. As described 
in Paper~2, for any given cluster, the necessary ingredients for the non-thermal emission 
model are mass, temperature, and gas density distribution. We assign to
each cluster in that simulation a gas density profile that is phenomenologically
constructed from state-of-art X-ray observations, as will be shown in
Section~\ref{sec:3}. In Section~4 and 5, we will show that this approach can successfully
reproduce the known X-ray cluster characteristics, such as the X-ray luminosity
function (XLF), the luminosity-mass relation, $L_{\rmn{X}}- M$, and the
$Y_{\rmn{X}}-M$ relation, where $Y_{\rmn{X}}=M_\rmn{gas}k_{\rmn{B}}T$ with an
X-ray-derived gas mass $M_{\rmn{gas}}$ and temperature $T$
\citep{2006ApJ...650..128K}. Moreover, we compare our $Y_{\rmn{SZ}}-M$ relation
with SZ-derived measurements. Only if our model matches available cluster data
on the gas properties, we can safely use it in Paper~2.} In this work, the cluster mass $M_{\Delta}$ 
and radius $R_{\Delta}$ are defined with respect to a density that is $\Delta=200$ or 
$\Delta=500$ times the \emph{critical} density of the Universe. We adopt density 
parameters of $\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$ and today's 
Hubble constant of $H_0 = 100 \times h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MultiDark simulation and final cluster sample}
\label{sec:2}
The MultiDark simulation used in this work is described in detail in \cite{2011arXiv1104.5130P}.  
It is an $N$-body cosmological simulation done with the Adaptive-Refinement-Tree (ART) 
code \citep{1997ApJS..111...73K} of $2048^3$ particles within a ($1000$~Mpc~$h^{-1}$)$^3$ 
cube. The adopted cosmological parameters are $\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$,
$\Omega_\rmn{b}=0.0469$, $n_\rmn{s}=0.95$, $h=0.7$ and $\sigma_8=0.82$. This simulation is 
particularly well suited for our purpose because of its large 
number of high-mass objects, i.e., galaxy clusters.

@@

{\bf In Paper~2, we present predictions for the LOFAR radio observatory
which is expected to detect diffuse radio emission in clusters up to redshift $z \approx 1$ (e.g.,
\citealp{2012JApA..tmp...34R}).} 
Thus, we make use of different simulation snapshots up to $z=1$. 
{\bf The extrapolation of our model beyond this redshift is rather uncertain as it is based
on observations at low(er) redshift.}
In Table~\ref{tab:z}, we show the total cluster number in our final cluster sample at different redshifts.

@@

\begin{figure} 
\centering
\includegraphics[width=0.48\textwidth]{figures/gas_profiles.eps}
\caption{Electron density profiles of the 31 clusters in the REXCESS sample. Grey and black lines represent NCCCs and CCCs, respectively. The blue and red lines represent our GNFW mean profile for the NCCCs and CCCs, respectively.}
\label{fig:gas_profiles}
\end{figure}

@@

\begin{figure*} 
\centering
\includegraphics[width=0.48\textwidth]{figures/lx_m.eps}
\includegraphics[width=0.48\textwidth]{figures/yx_m.eps}
%\includegraphics[width=0.33\textwidth]{figures/sz_m.eps}
\caption{X-ray scaling relations. Grey triangles show the MultiDark
  sample (limited to the mass range covered by observations), the black line is
  the corresponding scaling relation, and the blue line is the
  observational result. The black crosses represent the median values of the
  quantity in question for a given mass bin (indicated by horizontal error
  bars), and the vertical error bars represent the standard deviation within a
  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
  relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. 
  \emph{Right.} $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
  observational sample by \protect\cite{2010MNRAS.406.1773M}.} 
  %\emph{Right.} $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.2$ in comparison
  %to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
  %median redshift of about $0.18$. The bottom panels show the relative difference to
  %the observational scaling relations.}
\label{fig:X_LM}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{X-ray scaling relations and luminosity function}
\label{sec:4}

@@

In the right panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{X}}-M_{500}$ relation of our sample to observational data
\citep{2010MNRAS.406.1773M}. The model agrees nicely at the high-mass end, but
underpredicts the observed scaling at low masses by about $20\%$ (at the
1-$\sigma$ level). This is the same level of deviation from the data as in the
case of $L_{\rmn{X}}$, which is more significant due to the smaller scatter in
the $Y_{\rmn{X}}$ relation. The differential contribution to the thermal energy
per logarithmic interval in radius (and hence to the integrated Compton-$y$
parameter) is given by $\dd Y /\dd\log r \propto r^3 P_{\rmn{th}}(r)$, with the
thermal gas pressure $P_{\rmn{th}}=n_{\rmn{gas}}k_{\rmn{B}}T$. It peaks at
scales slightly smaller than $R_{500}$ with 1-$\sigma$ contributions extending
out to $3\,R_{500}$ \citep{2010ApJ...725...91B}. Hence, the observational
scaling constrains our model on those large scales, quite complementary to the
X-ray luminosity. The deviations at small masses either indicates different
assumptions about $f_{\rmn{gas}}$, the gas temperature, or different selection
effects of either observational sample that we use for model calibration and
comparison.  \cite{2010MNRAS.406.1773M} determine their masses by adopting a
constant value for $f_{\rmn{gas}}$, in contrast to our approach which adopts the
observed $f_{\rmn{gas},500}-M_{500}$ relation given by
\cite{2009ApJ...693.1142S}. Additionally, we adopt the
\cite{2010MNRAS.406.1773M} \emph{centrally included} temperature throughout all
our work, while \cite{2010MNRAS.406.1773M} use the \emph{centrally excised}
temperature to calculate $Y_{\rmn{X}}$. This assumption also impacts the scatter
of the $Y_{\rmn{X}}-M$ relation. In fact, using the \emph{centrally included}
temperature, we found a scatter of $\sigma_{yx} \approx 0.11$ (see
Table~\ref{tab:YXfits} where our $Y_{\rmn{X}}$ scaling relations are reported),
significantly higher than the value of $\sigma_{yx} = 0.052$ found by
\cite{2010MNRAS.406.1773M}.

@@

\subsection{X-ray Luminosity Function}
Studies of the XLF got out of fashion during the last years due to the
difficulties of using the X-ray luminosity for cosmological purposes. The X-ray
emissivity scales with the square of the gas density, which makes it subject to
density variations and clumping. This implies large scatter that causes a large
Malmquist bias and underlines the necessity of careful mock surveys that need to
address all systematics.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SZ scaling relations}
\label{sec:5}
In the right panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
\citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the 
\emph{Planck} COSMO sample with Malmquist bias correction (see their Table~A.1),
which has a median redshift of $0.18$. Hence, we compare the data to our relation 
at the MultiDark snapshot $z=0.2$}. Our model reproduces the data remarkably well, except 
for the high-mass end where our simulations have a weaker constraining power due to the 
smaller box size in comparison to the survey volume of {\em Planck}. We find a scatter of
$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
$\sigma_{yx} \approx 0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
relations for different redshifts.

\begin{figure} 
\centering
\includegraphics[width=0.48\textwidth]{figures/sz_m.eps}
\caption{SZ scaling relations. Grey triangles show the MultiDark
  sample (limited to the mass range covered by observations), the black line is
  the corresponding scaling relation, and the blue line is the
  observational result. The black crosses represent the median values of the
  quantity in question for a given mass bin (indicated by horizontal error
  bars), and the vertical error bars represent the standard deviation within a
  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
  relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. 
  \emph{Right.} $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
  observational sample by \protect\cite{2010MNRAS.406.1773M}. 
  \emph{Left.} $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.2$ in comparison
  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
  median redshift of about $0.18$. The bottom panels show the relative difference to
  the observational scaling relations.}
\label{fig:SZ_M}
\end{figure}

\begin{figure*} 
\centering
\includegraphics[width=0.48\textwidth]{figures/sz_m_SPT.eps}
\includegraphics[width=0.48\textwidth]{figures/sz_m_ACT.eps}
\caption{SZ scaling relations. Grey triangles show the MultiDark
  sample (limited to the mass range covered by observations), the black line is
  the corresponding scaling relation, and the blue line is the
  observational result. The black crosses represent the median values of the
  quantity in question for a given mass bin (indicated by horizontal error
  bars), and the vertical error bars represent the standard deviation within a
  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
  relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. 
  \emph{Right.} $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
  observational sample by \protect\cite{2010MNRAS.406.1773M}. 
  \emph{Left.} $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.2$ in comparison
  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
  median redshift of about $0.18$. The bottom panels show the relative difference to
  the observational scaling relations.}
\label{fig:SZ_M_1}
\end{figure*}

@@

{\bf We additionally compare our $Y_{\rmn{SZ}}$ to the results from the South Pole Telescope (SPT) 
and Atacama Cosmology Telescope (ACT) surveys.
We select a subsample of SPT clusters from \cite{2013ApJ...763..127R}, formed by the
115 objects with confirmed redshift and signal-to-noise above 5, which has a median
redshift of 0.56 with rms of 0.27. \cite{2013ApJ...763..127R} provide $Y_{\rmn{SZ}}$ 
within an aperture of $1'$, corresponding to a median radius of $0.2$~h$_{70}^{-1}$~Mpc 
at $z = 0.56$, which we use as aperture to calculate $Y_{\rmn{SZ, SPT}}$ in our MultiDark sample.

In the left panel of Fig.~\ref{fig:SZ_M_1}, we compare the SPT cluster subsample to our 
scaling relation at the three different MutliDark snapshots of $z = 0.4$, $0.61$ 
and $0.78$. We color-coded the SPT clusters in order to show that the SPT 
selection function is nearly redshift-independent. The fact that the angular size of galaxy clusters 
decreases with redshift is an advantage for SPT due to its small beam, in fact, higher-redshift clusters 
are less confused by primary CMB fluctuations. This effect is inverse for \emph{Planck} due to its
larger beam. We can conclude that while our $Y_{\rmn{SZ}}-M_{500}$ scaling relation 
compare fairly well to the median SPT cluster population, the SPT sample has a too
large scatter to be well represented by single MultiDark snapshots.

In the right panel of Fig.~\ref{fig:SZ_M_1}, we compare our scaling relation to
the ACT sample overlapping with the Sloan Digital Sky Survey stripe 82 
(\citealp{2013JCAP...07..008H}; we use the quantities inferred from the
universal pressure profile scaling relation).
The sample has a median redshift of 0.58 with rms of 0.28.
\cite{2013JCAP...07..008H} provides $Y_{\rmn{SZ}}$ within $R_{500}$ which
median, $0.42$~h$_{70}^{-1}$~Mpc, is, however, almost half of ours at the
MultiDark snapshot $z=0.61$. Therefore, we use an aperture of $0.42$~h$_{70}^{-1}$~Mpc
to calculate our $Y_{\rmn{SZ, ACT}}$. Also in this case we can conclude
that our mock sample reproduce fairly well the median observational sample. 
Note, however, the very different scatter of SPT and ACT samples.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}
We thank Anders Pinzke for many useful discussions. We also thank Harald Ebeling, 
Stefan Gottl{\"o}berg, Anatoly Klypin, Andrey Kravtsov, Adam Mantz, Frazer Pearce, 
Jos\'e Alberto Rubi\~no, and Gustavo Yepes, for the useful discussions and advices. 
Finally, we thank the MultiDark database people, in particular Adrian Partl and Kristin Riebe. 
F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of the 
program ``Junta para la Ampliaci\'on de Estudios'' co-financed by the FSE. 
F.Z.{\ }acknowledges the hospitality of the Leiden Observatory during his stay.
F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's Consolider-Ingenio 2010 Programme under
grant MultiDark CSD2009-00064. C.P.{\ }gratefully acknowledges financial support
of the Klaus Tschira Foundation. The MultiDark Database used in this paper and
the web application providing online access to it were constructed as part of
the activities of the German Astrophysical Virtual Observatory as result of a
collaboration between the Leibniz-Institute for Astrophysics Potsdam (AIP) and
the Spanish MultiDark Consolider Project CSD2009-00064. The Bolshoi and
MultiDark simulations were run on the NASA's Pleiades supercomputer at the NASA
Ames Research Center.
